---
title: "Machine Learning - Project Assignment"
author: "Luiz Bergo"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(taRifx)
library(skimr)
library(caret)
library(rpart)
library(parallel)
library(doParallel)
```

## Intro

At the present days wearable devices such as *Jawbone Up*, *Nike FuelBand*, and *Fitbit* let us gather a lot of information that can be processed to identify manners, behaviors and actions of users. Some of the findings understandign such information can be used to improve health in general.  

The researches invited 6 participants to use mobile devices on belt, forearm, arm, and dumbell. The accelerometers inforamtion were recorded and the participants should correctly identify their activities in 5 classes.   

Machine learning technics were applied to data aiming to correctly classify the activities according to the participants.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Many thanks to PUC-Rio who generous share the data used to train and validate this model, available at: <http://groupware.les.inf.puc-rio.br/har>
